PMV formulations: which one is the most accurate?

### 2022-06-15 Manuscript/src/sections/introduction.tex
paper: working on first draft

%! Author = sbbfti
%! Date = 10/06/2020

@@

    In 1970, Fanger~\cite{Fanger1970} developed the \ac{pmv} model, which is now incorporated into the \gls{7730} Standard~\cite{iso7730} in its original form.
    The \ac{pmv} model has been widely adopted worldwide both among researchers and practitioners.
    The \ac{pmv} is the most extensively used thermal comfort index for estimating the thermal sensation of a group of people sharing the same thermal environment.
    However, Cheung et al. (2019) demonstrated that the accuracy of the \ac{pmv} in predicting self-reported thermal sensation of people is only \qty{34}{\percent}~\cite{Cheung2019}.

    To overcome this problem, the \gls{55} Standard introduced a modified version of the \ac{pmv}, the \gls{pmv-ce}~\cite{ashrae552020}.
    For \ac{v} higher than \qty{0.1}{\m\per\s} the \gls{55} prescribes the use of the \ac{ce}.
    The value of \ac{ce}, calculated using the \ac{set} equation, is subtracted from both the value of \ac{tdb} and \ac{tr} and these results become the input into the \ac{pmv} model.
    The \ac{ce} already accounts for convective heat losses from the person to the environment, thus, the value of \ac{v}, used to calculate the \ac{pmv}, is set to \qty{0.1}{\m\per\s}.
    The other three input parameters (\ac{clo}, \ac{met}, and \ac{rh}) are not modified.
    Consequently, given the same thermal environment and same occupants, results from the two \ac{pmv} formulation differ when the value of \ac{v} is higher than \qty{0.1}{\m\per\s}.
    This may be a source of confusion for many users worldwide since both the \gls{7730} and the \gls{55} are the widely adopted and incorporated in many national building codes worldwide.
    In addition, over the course of the last \num{50} years, other formulations of the \ac{pmv} model have been formulated by other researchers.
    To our knowledge, no other study compared the accuracy all the aforementioned  two aforementioned PMV models.
    One study compared the accuracy of the \ac{pmv-ce} and the \ac{pmv} model.

>>>>

@@

In 1970, Fanger~\cite{Fanger1970} developed the \ac{pmv} model, which is now incorporated into the \gls{7730} Standard~\cite{iso7730} in its original form.
The \ac{pmv} model has been widely adopted worldwide both among researchers and practitioners.
It is the most extensively used thermal comfort index for estimating the thermal sensation of a group of people sharing the same thermal environment.
However, it has a relatively low accuracy in predicting self-reported thermal sensation of people~\cite{Cheung2019}.

To overcome this problem, the \gls{55} Standard uses a modified version of the original model developed by Fanger, the \gls{pmv-ce}~\cite{ashrae552020}.
For \ac{v} higher than \qty{0.1}{\m\per\s} the \gls{55} prescribes the use of the \ac{ce}.
The value of \ac{ce}, which is calculated using the \ac{set} equation, is subtracted from both the value of \ac{tdb} and \ac{tr}.
The resulting values become the new inputs into the \ac{pmv} model.
The \ac{ce} accounts for convective heat losses from the person to the environment, thus, the value of \ac{v}, used to calculate the \ac{pmv}, is set to \qty{0.1}{\m\per\s}.
While the other three input parameters (\ac{clo}, \ac{met}, and \ac{rh}) remain unchanged.
Consequently, for a given thermal environment, results from the two \ac{pmv} formulation differ when the value of \ac{v} is higher than \qty{0.1}{\m\per\s}.
This is a source of confusion for many users worldwide since both the \gls{7730} and the \gls{55} are the widely adopted and incorporated in many national and international building codes worldwide.
To further complicate this issue, over the course of the last \num{50} years, several other formulations of the \ac{pmv} model have been proposed.
Among the most notable formulations there are the:
\begin{enumerate}
    \item \gls{epmv}
    \item \gls{apmv}
    \item SET \ac{pmv}
    \item Gagge \ac{pmv}
    \item Marcel \ac{pmv}
\end{enumerate}

In 2002, Fanger, P. O. and Toftum, J. developed the \gls{epmv} an extension of the \ac{pmv}.
The \gls{epmv} includes an expectancy factor introduced for use in non-air-conditioned buildings in warm climates.
The authors argued that people adapt to the warm environment by decreasing their \ac{met} rate.
They, consequently, propose to reduce the metabolic rate used to calculate the \ac{pmv} by \qty{6.7}{\percent} for every scale unit of \ac{pmv} above neutral.
The resulting \ac{pmv} value is multiplied by the \ac{ef}.
The \ac{ef} for non-air-conditioned buildings can be determined by the length of warm weather throughout the year and whether such buildings may be compared to many others in the region that are air-conditioned.
If the temperature is hot all year or most of the year and there are no or few other air-conditioned buildings, \ac{ef} may be \num{0.5}, but if there are many other air-conditioned buildings, \ac{ef} may be \num{0.7}.
For non-air-conditioned buildings in locations where the temperature is warm solely during the summer and no or few buildings have air-conditioning \ac{ef} is \numrange{0.7}{0.8}, whereas it is \numrange{0.8}{.9} in areas where there are numerous air-conditioned buildings.
In regions with only brief periods of warm weather during the summer, the expectancy factor may be \numrange{0.9}{1}.
To better account for occupants adaptation Yao, R. et al. (2009) developed the Adaptive Predicted Mean
 Vote Model~\gls{apmv}.
They used a ``Black Box'' model to determine an adaptive coefficient which is in turn use to calculate the \gls{apmv} using the following equation: $\mathrm{aPMV} = \mathrm{PMV}/(1+\lambda \mathrm{PMV})$
The main issue with this approach is that the adaptive coefficient cannot be known a priori, but it is estimated based on the \ac{tsv} collected by a cohort of participants.

To our knowledge, no other study compared the accuracy all the aforementioned two aforementioned PMV models.
One study compared the accuracy of the \gls{pmv-ce} and the \ac{pmv} model.

### 2022-06-15 Manuscript/src/sections/titleAbstract.tex
paper: working on first draft

    \begin{abstract}
        The \ac{pmv} model was originally developed by Fanger to predict the thermal sensation of a large group of occupants sharing the same thermal environment.
        His model has seen widespread adoption and it is currently used in the \gls{7730}.
        However, to compensate for the model low prediction accuracy several other formulations have been proposed, one of which is currently used in the \gls{55}.
        This is a source of confusion for many practitioners and researchers who find it difficult to settle on which formulation they should use.
        We aim to solve this problem by comparing the accuracy of the main \ac{pmv} formulations against \var{tot_surveys} thermal sensation votes collected in buildings.
        % We found that for V>0.1m/s the \gls{pmv-ce} is significantly more accurate (48%) than the PMV (42%) in predicting thermal neutrality.
        % In 95% of the cases, the error was less than one point.
        % The PMV and PMVCE accuracy were 35% and 36% for |PMV|≤2 and 43% and 44% for |PMV|≤1, respectively.
        % Neither PMV model could accurately predict ‘cold’, ‘cool’, ‘warm’, or ‘hot’ thermal sensations.
        % Consequently, the PMV should only be used in conditions close to neutrality within the range |PMV|≤1.
        % We open-sourced the source code.
    \end{abstract}

>>>>

    \begin{abstract}
        The \ac{pmv} model was originally developed by Fanger to predict the thermal sensation of a large group of occupants sharing the same thermal environment.
        It has seen widespread adoption and it is currently used in the \gls{7730}.
        However, to compensate for the model low prediction accuracy, several other formulations have been proposed, one of which is currently used in the \gls{55}.
        This is a source of confusion for practitioners and researchers who find it difficult to decide which formulation to use.
        We aim to solve this problem by comparing the accuracy of the main \ac{pmv} formulations against \var{tot_surveys} thermal sensation votes collected in buildings.
        % We found that for V>0.1m/s the \gls{pmv-ce} is significantly more accurate (48%) than the PMV (42%) in predicting thermal neutrality.
        % In 95% of the cases, the error was less than one point.
        % The PMV and PMVCE accuracy were 35% and 36% for |PMV|≤2 and 43% and 44% for |PMV|≤1, respectively.
        % Neither PMV model could accurately predict ‘cold’, ‘cool’, ‘warm’, or ‘hot’ thermal sensations.
        % Consequently, the PMV should only be used in conditions close to neutrality within the range |PMV|≤1.
        % We open-sourced the source code.
    \end{abstract}
